---
title: "Predicting Situational Time On Ice"
author: "Kyle Joecken"
output: pdf_document
---

```{r, include = FALSE}
library(knitr)
opts_chunk$set(message = FALSE, warning = FALSE)
```

## Question

Can we use data from previous seasons to predict how much time a particular NHL
skater will get on the ice (TOI) in various situations (even strength,
short-handed, power play) in the upcoming 2014-2015 season?

## Data

As before, we load our database of season-wide NHL data into a data frame called
`skaterstats`.  We'll also grab our games played predictions and store it in a
data frame called `skatpred15`; these two steps are done with the `setup.R` file.
Finally, we will load our previous model for games played (`GPModel`).

```{r, echo=FALSE, results='hide'}
source('~/workspace/NHL_regression/R/setup.R')
rm(skaters, conn, driv, rs)
skaterstats <- skaterstats[, -c(3:5, 38:41)]
```

## Feature Selection

We'd like to compare a few different attempts. First, we'd like to model time on
ice directly, with and without our predicted games played. Then, we'd like to 
model time on ice per game and multiply it by our predicted games played numbers
and compare the accuracy.

We'll start again by modelling even-strength TOI using all possible predictors,
then try to ascertain which are the most important factors.

```{r}
gbmdata <- nhlShape(2012, 2013, outcome = 38)
rfdata <- nhlShape(2013, 2013, outcome = 38)
```

First, we build random forest models from several seeds.

```{r}
esrfmod1 <- nhlBuild(data = rfdata, perc = 0.7, seed = 9112)
esrfmod2 <- nhlBuild(data = rfdata, perc = 0.7, seed = 2857)
esrfmod3 <- nhlBuild(data = rfdata, perc = 0.7, seed = 31415)
esrfmod4 <- nhlBuild(data = rfdata, perc = 0.7, seed = 28182)
```

```{r, echo=FALSE}
varImpPlot(esrfmod1)
varImpPlot(esrfmod2)
varImpPlot(esrfmod3)
varImpPlot(esrfmod4)
```

```{r, results='hide'}
esgbmmod1 <- nhlBuild(data = gbmdata, type = "gbm", perc = 0.7, seed = 9112, n.trees = 10000, cv.folds = 5, n.cores = 4)
esgbmmod2 <- nhlBuild(data = gbmdata, type = "gbm", perc = 0.7, seed = 2857, n.trees = 10000, cv.folds = 5, n.cores = 4)
esgbmmod3 <- nhlBuild(data = gbmdata, type = "gbm", perc = 0.7, seed = 31415, n.trees = 10000, cv.folds = 5, n.cores = 4)
esgbmmod4 <- nhlBuild(data = gbmdata, type = "gbm", perc = 0.7, seed = 28182, n.trees = 10000, cv.folds = 5, n.cores = 4)
```

```{r, echo=FALSE}
sum1 <- as.data.frame(summary(esgbmmod1, plotit=FALSE))
sum2 <- as.data.frame(summary(esgbmmod2, plotit=FALSE))
sum3 <- as.data.frame(summary(esgbmmod3, plotit=FALSE))
sum4 <- as.data.frame(summary(esgbmmod4, plotit=FALSE))
sum <- merge(sum1, sum2, by = 1)
names(sum) <- c("var", "var.inf.1", "var.inf.2")
sum <- merge(sum, sum3, by = 1)
names(sum)[4] <- "var.inf.3"
sum <- merge(sum, sum4, by = 1)
names(sum)[5] <- "var.inf.4"
sum$var.inf.tot <- sum$var.inf.1 + sum$var.inf.2 + sum$var.inf.3 + sum$var.inf.4
sum <- sum[order(sum$var.inf.tot, decreasing = TRUE), ]
sumout <- sum[sum$var.inf.tot > 4, c(1, 6)]
row.names(sumout) <- NULL
print(sumout)
```

```{r}
col1 <- c(1:3, 15, 24, 30:31, 38:41)
col2 <- c(28:29, 32)
esDataRF1 <- nhlShape(2013, 2013, cols = c(col1, col2[1]), outcome = 38, rm.nhlnum = F)
esDataRF2 <- nhlShape(2013, 2013, cols = c(col1, col2[2]), outcome = 38, rm.nhlnum = F)
esDataRF3 <- nhlShape(2013, 2013, cols = c(col1, col2[3]), outcome = 38, rm.nhlnum = F)
esDataRF4 <- nhlShape(2013, 2013, cols = c(col1, col2), outcome = 38, rm.nhlnum = F)
esDataGBM1 <- nhlShape(2012, 2013, cols = c(col1, col2[1]), outcome = 38,
                       rm.nhlnum = F, rm.NA = FALSE)
esDataGBM1 <- subset(esDataGBM1, !is.na(games_played.1))
esDataGBM2 <- nhlShape(2012, 2013, cols = c(col1, col2[2]), outcome = 38,
                       rm.nhlnum = F, rm.NA = FALSE)
esDataGBM2 <- subset(esDataGBM2, !is.na(games_played.1))
esDataGBM3 <- nhlShape(2012, 2013, cols = c(col1, col2[3]), outcome = 38,
                       rm.nhlnum = F, rm.NA = FALSE)
esDataGBM3 <- subset(esDataGBM3, !is.na(games_played.1))
esDataGBM4 <- nhlShape(2012, 2013, cols = c(col1, col2), outcome = 38,
                       rm.nhlnum = F, rm.NA = FALSE)
esDataGBM4 <- subset(esDataGBM4, !is.na(games_played.1))
```

Here are the low level models.

```{r}
esrfmod1 <- nhlBuild(esDataRF1[, -1], perc = 1, seed = 77677)
esrfmod2 <- nhlBuild(esDataRF2[, -1], perc = 1)
esrfmod3 <- nhlBuild(esDataRF3[, -1], perc = 1)
esrfmod4 <- nhlBuild(esDataRF4[, -1], perc = 1)
esgbmmod1 <- nhlBuild(esDataGBM1[, -1], type = "gbm", perc = 1, n.trees = 10000, cv.folds = 5, n.cores = 4)
esgbmmod2 <- nhlBuild(esDataGBM2[, -1], type = "gbm", perc = 1, n.trees = 10000, cv.folds = 5, n.cores = 4)
esgbmmod3 <- nhlBuild(esDataGBM3[, -1], type = "gbm", perc = 1, n.trees = 10000, cv.folds = 5, n.cores = 4)
esgbmmod4 <- nhlBuild(esDataGBM4[, -1], type = "gbm", perc = 1, n.trees = 10000, cv.folds = 5, n.cores = 4)
```

We build our data frame with the low level predictions in it.

```{r}
esrf1 <- predict(esrfmod1, esDataRF1)
esrf2 <- predict(esrfmod2, esDataRF2)
esrf3 <- predict(esrfmod3, esDataRF3)
esrf4 <- predict(esrfmod4, esDataRF4)
esrf <- as.data.frame(cbind(esDataRF1[, 1], esrf1, esrf2, esrf3, esrf4))
names(esrf) <- c("nhl_num", "esrf1", "esrf2", "esrf3", "esrf4")
esgbm1 <- predict(esgbmmod1, esDataGBM1)
esgbm2 <- predict(esgbmmod2, esDataGBM2)
esgbm3 <- predict(esgbmmod3, esDataGBM3)
esgbm4 <- predict(esgbmmod4, esDataGBM4)
esgbm <- as.data.frame(cbind(esDataGBM1[, 1], esgbm1, esgbm2, esgbm3, esgbm4))
names(esgbm) <- c("nhl_num", "esgbm1", "esgbm2", "esgbm3", "esgbm4")
esData <- merge(esrf, esgbm, all = TRUE)
esData <- merge(esData, esDataGBM1[, c(1, 22)])
```

The final even strength model is built.

```{r}
esModel <- nhlBuild(esData[, -1], type = "gbm", perc = 0.7, seed = 98765, n.trees = 10000, cv.folds = 5, n.cores = 4)
```

We repeat the overall process for short-handed time next.

```{r}
gbmdata <- nhlShape(2012, 2013, outcome = 39)
rfdata <- nhlShape(2013, 2013, outcome = 39)
```

```{r}
shrfmod1 <- nhlBuild(data = rfdata, perc = 0.7, seed = 9112)
shrfmod2 <- nhlBuild(data = rfdata, perc = 0.7, seed = 2857)
shrfmod3 <- nhlBuild(data = rfdata, perc = 0.7, seed = 31415)
shrfmod4 <- nhlBuild(data = rfdata, perc = 0.7, seed = 28182)
```

```{r, echo=FALSE}
varImpPlot(shrfmod1)
varImpPlot(shrfmod2)
varImpPlot(shrfmod3)
varImpPlot(shrfmod4)
```

```{r, results='hide'}
shgbmmod1 <- nhlBuild(data = gbmdata, type = "gbm", perc = 0.7, seed = 9112, n.trees = 10000, cv.folds = 5, n.cores = 4)
shgbmmod2 <- nhlBuild(data = gbmdata, type = "gbm", perc = 0.7, seed = 2857, n.trees = 10000, cv.folds = 5, n.cores = 4)
shgbmmod3 <- nhlBuild(data = gbmdata, type = "gbm", perc = 0.7, seed = 31415, n.trees = 10000, cv.folds = 5, n.cores = 4)
shgbmmod4 <- nhlBuild(data = gbmdata, type = "gbm", perc = 0.7, seed = 28182, n.trees = 10000, cv.folds = 5, n.cores = 4)
```

```{r, echo=FALSE}
sum1 <- as.data.frame(summary(shgbmmod1, plotit=FALSE))
sum2 <- as.data.frame(summary(shgbmmod2, plotit=FALSE))
sum3 <- as.data.frame(summary(shgbmmod3, plotit=FALSE))
sum4 <- as.data.frame(summary(shgbmmod4, plotit=FALSE))
sum <- merge(sum1, sum2, by = 1)
names(sum) <- c("var", "var.inf.1", "var.inf.2")
sum <- merge(sum, sum3, by = 1)
names(sum)[4] <- "var.inf.3"
sum <- merge(sum, sum4, by = 1)
names(sum)[5] <- "var.inf.4"
sum$var.inf.tot <- sum$var.inf.1 + sum$var.inf.2 + sum$var.inf.3 + sum$var.inf.4
sum <- sum[order(sum$var.inf.tot, decreasing = TRUE), ]
sumout <- sum[sum$var.inf.tot > 4, c(1, 6)]
row.names(sumout) <- NULL
print(sumout)
```

Both models seem to agree; the previous season's `sh_toi` is far and away the best predictor, with `team_pp_goals_against` making
a surprising showing in second place.  Perhaps there is a possession argument to be made for the inclusion of this factor.

Unsurprising entries that show up every time are remaining TOI stats and `blocked_shots`.  Additional factors of value that show
up consistently in random forest models are `team_goals_against`, `giveaways`, and `points`; we'll use these as minor factors.

This is going to be quite the simple model.

```{r}
col1 <- c(1:2, 27, 29, 38:41)
col2 <- c(6, 26, 31)
shDataRF1 <- nhlShape(2013, 2013, cols = c(col1, col2[1]), outcome = 39, rm.nhlnum = F)
shDataRF2 <- nhlShape(2013, 2013, cols = c(col1, col2[2]), outcome = 39, rm.nhlnum = F)
shDataRF3 <- nhlShape(2013, 2013, cols = c(col1, col2[3]), outcome = 39, rm.nhlnum = F)
shDataRF4 <- nhlShape(2013, 2013, cols = c(col1, col2), outcome = 39, rm.nhlnum = F)
shDataGBM1 <- nhlShape(2012, 2013, cols = c(col1, col2[1]), outcome = 39,
                       rm.nhlnum = F, rm.NA = FALSE)
shDataGBM1 <- subset(shDataGBM1, !is.na(sh_toi.1))
shDataGBM2 <- nhlShape(2012, 2013, cols = c(col1, col2[2]), outcome = 39,
                       rm.nhlnum = F, rm.NA = FALSE)
shDataGBM2 <- subset(shDataGBM2, !is.na(sh_toi.1))
shDataGBM3 <- nhlShape(2012, 2013, cols = c(col1, col2[3]), outcome = 39,
                       rm.nhlnum = F, rm.NA = FALSE)
shDataGBM3 <- subset(shDataGBM3, !is.na(sh_toi.1))
shDataGBM4 <- nhlShape(2012, 2013, cols = c(col1, col2), outcome = 39,
                       rm.nhlnum = F, rm.NA = FALSE)
shDataGBM4 <- subset(shDataGBM4, !is.na(sh_toi.1))
```

Here are the low level models.

```{r}
shrfmod1 <- nhlBuild(shDataRF1[, -1], perc = 1, seed = 77677)
shrfmod2 <- nhlBuild(shDataRF2[, -1], perc = 1)
shrfmod3 <- nhlBuild(shDataRF3[, -1], perc = 1)
shrfmod4 <- nhlBuild(shDataRF4[, -1], perc = 1)
shgbmmod1 <- nhlBuild(shDataGBM1[, -1], type = "gbm", perc = 1, n.trees = 10000, cv.folds = 5, n.cores = 4)
shgbmmod2 <- nhlBuild(shDataGBM2[, -1], type = "gbm", perc = 1, n.trees = 10000, cv.folds = 5, n.cores = 4)
shgbmmod3 <- nhlBuild(shDataGBM3[, -1], type = "gbm", perc = 1, n.trees = 10000, cv.folds = 5, n.cores = 4)
shgbmmod4 <- nhlBuild(shDataGBM4[, -1], type = "gbm", perc = 1, n.trees = 10000, cv.folds = 5, n.cores = 4)
```

We build our data frame with the low level predictions in it.

```{r}
shrf1 <- predict(shrfmod1, shDataRF1)
shrf2 <- predict(shrfmod2, shDataRF2)
shrf3 <- predict(shrfmod3, shDataRF3)
shrf4 <- predict(shrfmod4, shDataRF4)
shrf <- as.data.frame(cbind(shDataRF1[, 1], shrf1, shrf2, shrf3, shrf4))
names(shrf) <- c("nhl_num", "shrf1", "shrf2", "shrf3", "shrf4")
shgbm1 <- predict(shgbmmod1, shDataGBM1)
shgbm2 <- predict(shgbmmod2, shDataGBM2)
shgbm3 <- predict(shgbmmod3, shDataGBM3)
shgbm4 <- predict(shgbmmod4, shDataGBM4)
shgbm <- as.data.frame(cbind(shDataGBM1[, 1], shgbm1, shgbm2, shgbm3, shgbm4))
names(shgbm) <- c("nhl_num", "shgbm1", "shgbm2", "shgbm3", "shgbm4")
shData <- merge(shrf, shgbm, all = TRUE)
shData <- merge(shData, shDataGBM1[, c(1, 16)])
```

The final short-handed model is built.

```{r}
shModel <- nhlBuild(shData[, -1], type = "gbm", perc = 0.7, seed = 98765, n.trees = 10000, cv.folds = 5, n.cores = 4)
```

And once more for the power play.

```{r}
gbmdata <- nhlShape(2012, 2013, outcome = 40)
rfdata <- nhlShape(2013, 2013, outcome = 40)
```

```{r}
pprfmod1 <- nhlBuild(data = rfdata, perc = 0.7, seed = 9112)
pprfmod2 <- nhlBuild(data = rfdata, perc = 0.7, seed = 2857)
pprfmod3 <- nhlBuild(data = rfdata, perc = 0.7, seed = 31415)
pprfmod4 <- nhlBuild(data = rfdata, perc = 0.7, seed = 28182)
```

```{r, echo=FALSE}
varImpPlot(pprfmod1)
varImpPlot(pprfmod2)
varImpPlot(pprfmod3)
varImpPlot(pprfmod4)
```

```{r, results='hide'}
ppgbmmod1 <- nhlBuild(data = gbmdata, type = "gbm", perc = 0.7, seed = 9112, n.trees = 10000, cv.folds = 5, n.cores = 4)
ppgbmmod2 <- nhlBuild(data = gbmdata, type = "gbm", perc = 0.7, seed = 2857, n.trees = 10000, cv.folds = 5, n.cores = 4)
ppgbmmod3 <- nhlBuild(data = gbmdata, type = "gbm", perc = 0.7, seed = 31415, n.trees = 10000, cv.folds = 5, n.cores = 4)
ppgbmmod4 <- nhlBuild(data = gbmdata, type = "gbm", perc = 0.7, seed = 28182, n.trees = 10000, cv.folds = 5, n.cores = 4)
```

```{r, echo=FALSE}
sum1 <- as.data.frame(summary(ppgbmmod1, plotit=FALSE))
sum2 <- as.data.frame(summary(ppgbmmod2, plotit=FALSE))
sum3 <- as.data.frame(summary(ppgbmmod3, plotit=FALSE))
sum4 <- as.data.frame(summary(ppgbmmod4, plotit=FALSE))
sum <- merge(sum1, sum2, by = 1)
names(sum) <- c("var", "var.inf.1", "var.inf.2")
sum <- merge(sum, sum3, by = 1)
names(sum)[4] <- "var.inf.3"
sum <- merge(sum, sum4, by = 1)
names(sum)[5] <- "var.inf.4"
sum$var.inf.tot <- sum$var.inf.1 + sum$var.inf.2 + sum$var.inf.3 + sum$var.inf.4
sum <- sum[order(sum$var.inf.tot, decreasing = TRUE), ]
sumout <- sum[sum$var.inf.tot > 4, c(1, 6)]
row.names(sumout) <- NULL
print(sumout)
```

Not surprisingly, overall and power play offensive metrics reign supreme here.  In particular,
team success metrics (*e.g.*, `team_goals_for`) are important.

Shot statistics and points have lesser importance to both models types, and we also add
`games_played` and `es_toi` from the random forest importance graphs as second-tier
predictors.

```{r}
col1 <- c(1:2, 5, 10, 24:25, 40)
col2 <- c(3, 6, 15, 30, 38)
ppDataRF1 <- nhlShape(2013, 2013, cols = c(col1, col2[1]), outcome = 40, rm.nhlnum = F)
ppDataRF2 <- nhlShape(2013, 2013, cols = c(col1, col2[2]), outcome = 40, rm.nhlnum = F)
ppDataRF3 <- nhlShape(2013, 2013, cols = c(col1, col2[3]), outcome = 40, rm.nhlnum = F)
ppDataRF4 <- nhlShape(2013, 2013, cols = c(col1, col2[4]), outcome = 40, rm.nhlnum = F)
ppDataRF5 <- nhlShape(2013, 2013, cols = c(col1, col2[5]), outcome = 40, rm.nhlnum = F)
ppDataRF6 <- nhlShape(2013, 2013, cols = c(col1, col2), outcome = 40, rm.nhlnum = F)
ppDataGBM1 <- nhlShape(2012, 2013, cols = c(col1, col2[1]), outcome = 40,
                       rm.nhlnum = F, rm.NA = FALSE)
ppDataGBM1 <- subset(ppDataGBM1, !is.na(pp_toi.1))
ppDataGBM2 <- nhlShape(2012, 2013, cols = c(col1, col2[2]), outcome = 40,
                       rm.nhlnum = F, rm.NA = FALSE)
ppDataGBM2 <- subset(ppDataGBM2, !is.na(pp_toi.1))
ppDataGBM3 <- nhlShape(2012, 2013, cols = c(col1, col2[3]), outcome = 40,
                       rm.nhlnum = F, rm.NA = FALSE)
ppDataGBM3 <- subset(ppDataGBM3, !is.na(pp_toi.1))
ppDataGBM4 <- nhlShape(2012, 2013, cols = c(col1, col2[4]), outcome = 40,
                       rm.nhlnum = F, rm.NA = FALSE)
ppDataGBM4 <- subset(ppDataGBM4, !is.na(pp_toi.1))
ppDataGBM5 <- nhlShape(2012, 2013, cols = c(col1, col2[5]), outcome = 40,
                       rm.nhlnum = F, rm.NA = FALSE)
ppDataGBM5 <- subset(ppDataGBM5, !is.na(pp_toi.1))
ppDataGBM6 <- nhlShape(2012, 2013, cols = c(col1, col2), outcome = 40,
                       rm.nhlnum = F, rm.NA = FALSE)
ppDataGBM6 <- subset(ppDataGBM6, !is.na(pp_toi.1))
```

Here are the low level models.

```{r}
pprfmod1 <- nhlBuild(ppDataRF1[, -1], perc = 1, seed = 77677)
pprfmod2 <- nhlBuild(ppDataRF2[, -1], perc = 1)
pprfmod3 <- nhlBuild(ppDataRF3[, -1], perc = 1)
pprfmod4 <- nhlBuild(ppDataRF4[, -1], perc = 1)
pprfmod5 <- nhlBuild(ppDataRF5[, -1], perc = 1)
pprfmod6 <- nhlBuild(ppDataRF6[, -1], perc = 1)
ppgbmmod1 <- nhlBuild(ppDataGBM1[, -1], type = "gbm", perc = 1, n.trees = 10000, cv.folds = 5, n.cores = 4)
ppgbmmod2 <- nhlBuild(ppDataGBM2[, -1], type = "gbm", perc = 1, n.trees = 10000, cv.folds = 5, n.cores = 4)
ppgbmmod3 <- nhlBuild(ppDataGBM3[, -1], type = "gbm", perc = 1, n.trees = 10000, cv.folds = 5, n.cores = 4)
ppgbmmod4 <- nhlBuild(ppDataGBM4[, -1], type = "gbm", perc = 1, n.trees = 10000, cv.folds = 5, n.cores = 4)
ppgbmmod5 <- nhlBuild(ppDataGBM5[, -1], type = "gbm", perc = 1, n.trees = 10000, cv.folds = 5, n.cores = 4)
ppgbmmod6 <- nhlBuild(ppDataGBM6[, -1], type = "gbm", perc = 1, n.trees = 10000, cv.folds = 5, n.cores = 4)
```

We build our data frame with the low level predictions in it.

```{r}
pprf1 <- predict(pprfmod1, ppDataRF1)
pprf2 <- predict(pprfmod2, ppDataRF2)
pprf3 <- predict(pprfmod3, ppDataRF3)
pprf4 <- predict(pprfmod4, ppDataRF4)
pprf5 <- predict(pprfmod5, ppDataRF5)
pprf6 <- predict(pprfmod6, ppDataRF6)
pprf <- as.data.frame(cbind(ppDataRF1[, 1], pprf1, pprf2, pprf3, pprf4, pprf5, pprf6))
names(pprf) <- c("nhl_num", "pprf1", "pprf2", "pprf3", "pprf4", "pprf5", "pprf6")
ppgbm1 <- predict(ppgbmmod1, ppDataGBM1)
ppgbm2 <- predict(ppgbmmod2, ppDataGBM2)
ppgbm3 <- predict(ppgbmmod3, ppDataGBM3)
ppgbm4 <- predict(ppgbmmod4, ppDataGBM4)
ppgbm5 <- predict(ppgbmmod5, ppDataGBM5)
ppgbm6 <- predict(ppgbmmod6, ppDataGBM6)
ppgbm <- as.data.frame(cbind(ppDataGBM1[, 1], ppgbm1, ppgbm2, ppgbm3, ppgbm4, ppgbm5, ppgbm6))
names(ppgbm) <- c("nhl_num", "ppgbm1", "ppgbm2", "ppgbm3", "ppgbm4", "ppgbm5", "ppgbm6")
ppData <- merge(pprf, ppgbm, all = TRUE)
ppData <- merge(ppData, ppDataGBM1[, c(1, 14)])
```

The power play time model is finally built.

```{r}
ppModel <- nhlBuild(ppData[, -1], type = "gbm", perc = 0.7, seed = 98765, n.trees = 10000, cv.folds = 5, n.cores = 4)
```

```{r, echo=FALSE, results='hide'}
rm(skaterstats, nhlAnalyze, nhlBuild, nhlModel, nhlShape)
rm(gbmdata, rfdata)
rm(sum1, sum2, sum3, sum4, sum, sumout)
rm(esDataRF1, esDataRF2, esDataRF3, esDataRF4, esDataGBM1, esDataGBM2, esDataGBM3, esDataGBM4)
rm(esrf1, esrf2, esrf3, esrf4, esrf)
rm(esgbm1, esgbm2, esgbm3, esgbm4, esgbm, esData)
rm(shDataRF1, shDataRF2, shDataRF3, shDataRF4, shDataGBM1, shDataGBM2, shDataGBM3, shDataGBM4)
rm(shrf1, shrf2, shrf3, shrf4, shrf)
rm(shgbm1, shgbm2, shgbm3, shgbm4, shgbm, shData)
rm(ppDataRF1, ppDataRF2, ppDataRF3, ppDataRF4, ppDataRF5, ppDataRF6)
rm(ppDataGBM1, ppDataGBM2, ppDataGBM3, ppDataGBM4, ppDataGBM5, ppDataGBM6)
rm(pprf1, pprf2, pprf3, pprf4, pprf5, pprf6, pprf)
rm(ppgbm1, ppgbm2, ppgbm3, ppgbm4, ppgbm5, ppgbm6, ppgbm, ppData)
rm(col1, col2)
```
