---
title: "Predicting Games Played"
author: "Kyle Joecken"
date: "09/29/2014"
output: pdf_document
---

## Question

Can we use games played data from the previous few National Hockey League (NHL) seasons to predict how many games a particular skater (*i.e.*, non-goalie) will play in an upcoming season?

In particular, the hope is that games played for various players in their more recently played seasons will help to predict how many games they'll play in future seasons.  This is quite difficult, as the data is exceedingly noisy due to the largely random nature of injuries in a fast-paced, full-contact sport.

## Data

First, we load the data from our local (scraped) database of season-wide NHL data.  It is stored in a data frame called `skaterstats`.

```{r, echo=FALSE, results='hide', include=FALSE}
library(RPostgreSQL)
driv <- dbDriver("PostgreSQL")
conn <- dbConnect(driv, dbname = "nhltest", user = "postgres", password = "hollyleaf", host = "localhost")
rs <- dbSendQuery(conn, statement = "SELECT * FROM skaterstats;")
skaterstats <- fetch(rs, n = -1)
dbClearResult(rs)
dbDisconnect(conn)
```

## Features

Next, we strip out all the unnecessary variables and reshape the data frame, so that each player (identified by their `nhl_num`, or the unique 7-digit number assigned to them by the NHL's website) is a unique observation.  Each observation will simply be a list of games played in various seasons. This will leave us with a column for each player called `games_played.####`, where the `####` is a season between 1998 and 2014.  We'll also scale up the 2013 season (in which only 48 games were played) by multiplying it by the factor $82/48$.

To get some idea of how the data relate to each other, we'll then plot each variable against each other using the function `pairs()`.  Looking at every single season against the others would be too many, so to get a glimpse of the data we'll first restrict to players that have played in each of the seasons from 1998 to 2002, then plot only those 5 against each other.  The data will obviously be tremendously noisy.

```{r}
skatergames <- skaterstats[, c(1, 2, 6)]
skatergames <- reshape(skatergames, timevar = "season",
                       idvar = "nhl_num", direction = "wide")
skatergames$games_played.2013 <- skatergames$games_played.2013 * 82 / 48
gp9802 <- skatergames[!is.na(skatergames$games_played.1998) &
                            !is.na(skatergames$games_played.1999) &
                            !is.na(skatergames$games_played.2000) &
                            !is.na(skatergames$games_played.2001) &
                            !is.na(skatergames$games_played.2002), 1:6]
pairs(gp9802[, 2:6])
```

Each of these plots contains `r length(gp9802$nhl_num)` points, so the sample sizes are still fairly large.  We see here that there is a large cluster of points in the top right corner, as most players play close to the full 82 in each season.

Next, we should fit a few linear regressions, adding progressively older seasons' data as new regressors.  We can then run a variance analysis to see if we're still getting any gains from each successively older season.

```{r}
fit1 <- lm(games_played.2002 ~ games_played.2001, data = gp9802)
fit2 <- lm(games_played.2002 ~ games_played.2001 + games_played.2000, data = gp9802)
fit3 <- lm(games_played.2002 ~ games_played.2001 + games_played.2000 + 
                 games_played.1999, data = gp9802)
fit4 <- lm(games_played.2002 ~ games_played.2001 + games_played.2000 + 
                 games_played.1999 + games_played.1998, data = gp9802)
anova(fit1, fit2, fit3, fit4)
```

With the low $p$-value for `fit4` and the realtively low $F$-value for `fit3`, it seems like `fit2` might be the most reasonable choice to go with of these options.

## Algorithm

What we'll do now is try to find a *usual* and simple set of coefficients across various regressions of the type `lm(gp.y+2 ~ gp.y+1 + gp.y)`, saving a prediction for `games_played.2014` as a test case.  We'll collect the coefficients in a matrix called `coeffs` and have a look when we've finished.

```{r, echo=FALSE}
gp9800 <- skatergames[!is.na(skatergames$games_played.1998) &
                            !is.na(skatergames$games_played.1999) &
                            !is.na(skatergames$games_played.2000), 1:4]
gp9901 <- skatergames[!is.na(skatergames$games_played.1999) &
                            !is.na(skatergames$games_played.2000) &
                            !is.na(skatergames$games_played.2001), c(1, 3:5)]
gp0002 <- skatergames[!is.na(skatergames$games_played.2000) &
                            !is.na(skatergames$games_played.2001) &
                            !is.na(skatergames$games_played.2002), c(1, 4:6)]
gp0103 <- skatergames[!is.na(skatergames$games_played.2001) &
                            !is.na(skatergames$games_played.2002) &
                            !is.na(skatergames$games_played.2003), c(1, 5:7)]
gp0204 <- skatergames[!is.na(skatergames$games_played.2002) &
                            !is.na(skatergames$games_played.2003) &
                            !is.na(skatergames$games_played.2004), c(1, 6:8)]
gp0306 <- skatergames[!is.na(skatergames$games_played.2003) &
                            !is.na(skatergames$games_played.2004) &
                            !is.na(skatergames$games_played.2006), c(1, 7:9)]
gp0407 <- skatergames[!is.na(skatergames$games_played.2004) &
                            !is.na(skatergames$games_played.2006) &
                            !is.na(skatergames$games_played.2007), c(1, 8:10)]
gp0608 <- skatergames[!is.na(skatergames$games_played.2006) &
                            !is.na(skatergames$games_played.2007) &
                            !is.na(skatergames$games_played.2008), c(1, 9:11)]
gp0709 <- skatergames[!is.na(skatergames$games_played.2007) &
                            !is.na(skatergames$games_played.2008) &
                            !is.na(skatergames$games_played.2009), c(1, 10:12)]
gp0810 <- skatergames[!is.na(skatergames$games_played.2008) &
                            !is.na(skatergames$games_played.2009) &
                            !is.na(skatergames$games_played.2010), c(1, 11:13)]
gp0911 <- skatergames[!is.na(skatergames$games_played.2009) &
                            !is.na(skatergames$games_played.2010) &
                            !is.na(skatergames$games_played.2011), c(1, 12:14)]
gp1012 <- skatergames[!is.na(skatergames$games_played.2010) &
                            !is.na(skatergames$games_played.2011) &
                            !is.na(skatergames$games_played.2012), c(1, 13:15)]
gp1113 <- skatergames[!is.na(skatergames$games_played.2011) &
                            !is.na(skatergames$games_played.2012) &
                            !is.na(skatergames$games_played.2013), c(1, 14:16)]
gp1214 <- skatergames[!is.na(skatergames$games_played.2012) &
                            !is.na(skatergames$games_played.2013) &
                            !is.na(skatergames$games_played.2014), c(1, 15:17)]
fit2000 <- lm(games_played.2000 ~ games_played.1999 +
                 games_played.1998, data = gp9800)
fit2001 <- lm(games_played.2001 ~ games_played.2000 +
                 games_played.1999, data = gp9901)
fit2002 <- lm(games_played.2002 ~ games_played.2001 +
                 games_played.2000, data = gp0002)
fit2003 <- lm(games_played.2003 ~ games_played.2002 +
                 games_played.2001, data = gp0103)
fit2004 <- lm(games_played.2004 ~ games_played.2003 +
                 games_played.2002, data = gp0204)
fit2006 <- lm(games_played.2006 ~ games_played.2004 +
                 games_played.2003, data = gp0306)
fit2007 <- lm(games_played.2007 ~ games_played.2006 +
                 games_played.2004, data = gp0407)
fit2008 <- lm(games_played.2008 ~ games_played.2007 +
                 games_played.2006, data = gp0608)
fit2009 <- lm(games_played.2009 ~ games_played.2008 +
                 games_played.2007, data = gp0709)
fit2010 <- lm(games_played.2010 ~ games_played.2009 +
                 games_played.2008, data = gp0810)
fit2011 <- lm(games_played.2011 ~ games_played.2010 +
                 games_played.2009, data = gp0911)
fit2012 <- lm(games_played.2012 ~ games_played.2011 +
                 games_played.2010, data = gp1012)
fit2013 <- lm(games_played.2013 ~ games_played.2012 +
                 games_played.2011, data = gp1113)
coeffs <- rbind(fit2000$coef, fit2001$coef, fit2002$coef, 
                fit2003$coef, fit2004$coef, fit2006$coef, 
                fit2007$coef, fit2008$coef, fit2009$coef, 
                fit2010$coef, fit2011$coef, fit2012$coef, fit2013$coef)
coeffs <- rbind(coeffs, colMeans(coeffs))
rownames(coeffs) <- c("98-00", "99-01", "00-02", "01-03", "02-04",
                       "03-06", "04-07", "06-08", "07-09", "08-10",
                       "09-11", "10-12", "11-13", "means")
colnames(coeffs) <- c("baseline", "season n-1", "season n-2")
coeffs
```

We therefore claim that if $x$ = `games_played.n`, $y$ = `games_played.n-1` and $z =$ `games.played.n-2` that $x \sim$ `r coeffs[14, 1]` + `r coeffs[14, 2]`$y$ + `r coeffs[14, 3]`$z$.

Alternatively, we could rewrite this equation by replacing $y$ and $z$ with $\bar{y}$ and $\bar{z}$, the number of games *missed* in seasons `n-1` and `n-2`, respectively.  This may be slightly more interpretable.  Making this replacement and rounding the coefficients to slightly nicer numbers, we get that

$$x \sim 73 - \frac{4\bar{y}}{9} - \frac{3\bar{z}}{20}.$$

Perhaps not surprisingly, these coefficients are not significantly far off from those achieved from another analysis done for NBA players, who also play an 82-game season.  Their coefficients where $76$, $\frac{1}{2}$ and $\frac{1}{6}$.  I'm searching for this source to include it; I saw it linked a few months ago by Nate Silver, but haven't been able to find it again.
