---
title: "Predicting Goals"
author: "Kyle Joecken"
date: "12/09/2014"
output: pdf_document
---

```{r, include = FALSE}
library(knitr)
opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r, echo=FALSE, results='hide'}
source('~/workspace/NHL_regression/R/setup.R')
skaterstats <- skaterstats[, -c(3:5, 38:41)]
```

We first calculate `es_goals`.

```{r}
skaterstats$es_goals <- skaterstats$goals - skaterstats$pp_goals - skaterstats$sh_goals
```

We build data sets with `es_goals` as the outcome,

```{r}
gbmdata <- nhlShape(2012, 2013, outcome = 42)
rfdata <- nhlShape(2013, 2013, outcome = 42)
```

and from them we build exploratory models.

```{r, cache=TRUE, results='hide'}
esGoalFactors <- nhlAnalyze(rfdata, gbmdata, seed = 61616)
```

Here are some collected factor statistics.

```{r, echo=FALSE}
print(esGoalFactors)
```

Plucking a set of first- and second-tier factors, we build focused data sets.

```{r}
col1 <- c(1:2, 4, 6, 15:16, 30, 32, 38:42)
col2 <- c(3, 24:25, 29, 33:34)
esgDataRF1 <- nhlShape(2013, 2013, cols = c(col1, col2[1]), outcome = 42, rm.nhlnum = F)
esgDataRF2 <- nhlShape(2013, 2013, cols = c(col1, col2[2]), outcome = 42, rm.nhlnum = F)
esgDataRF3 <- nhlShape(2013, 2013, cols = c(col1, col2[3]), outcome = 42, rm.nhlnum = F)
esgDataRF4 <- nhlShape(2013, 2013, cols = c(col1, col2[4]), outcome = 42, rm.nhlnum = F)
esgDataRF5 <- nhlShape(2013, 2013, cols = c(col1, col2[5]), outcome = 42, rm.nhlnum = F)
esgDataRF6 <- nhlShape(2013, 2013, cols = c(col1, col2[6]), outcome = 42, rm.nhlnum = F)
esgDataRF7 <- nhlShape(2013, 2013, cols = c(col1, col2), outcome = 42, rm.nhlnum = F)
esgDataGBM1 <- nhlShape(2012, 2013, cols = c(col1, col2[1]), outcome = 42,
                       rm.nhlnum = F, rm.NA = FALSE)
esgDataGBM1 <- subset(esgDataGBM1, !is.na(goals.1))
esgDataGBM2 <- nhlShape(2012, 2013, cols = c(col1, col2[2]), outcome = 42,
                       rm.nhlnum = F, rm.NA = FALSE)
esgDataGBM2 <- subset(esgDataGBM2, !is.na(goals.1))
esgDataGBM3 <- nhlShape(2012, 2013, cols = c(col1, col2[3]), outcome = 42,
                       rm.nhlnum = F, rm.NA = FALSE)
esgDataGBM3 <- subset(esgDataGBM3, !is.na(goals.1))
esgDataGBM4 <- nhlShape(2012, 2013, cols = c(col1, col2[4]), outcome = 42,
                       rm.nhlnum = F, rm.NA = FALSE)
esgDataGBM4 <- subset(esgDataGBM4, !is.na(goals.1))
esgDataGBM5 <- nhlShape(2012, 2013, cols = c(col1, col2[5]), outcome = 42,
                       rm.nhlnum = F, rm.NA = FALSE)
esgDataGBM5 <- subset(esgDataGBM5, !is.na(goals.1))
esgDataGBM6 <- nhlShape(2012, 2013, cols = c(col1, col2[6]), outcome = 42,
                       rm.nhlnum = F, rm.NA = FALSE)
esgDataGBM6 <- subset(esgDataGBM6, !is.na(goals.1))
esgDataGBM7 <- nhlShape(2012, 2013, cols = c(col1, col2), outcome = 42,
                       rm.nhlnum = F, rm.NA = FALSE)
esgDataGBM7 <- subset(esgDataGBM7, !is.na(goals.1))
```

We build our pre-models from them.

```{r, cache=TRUE, results='hide'}
esgrfmod1 <- nhlBuild(esgDataRF1[, -1], perc = 1, seed = 98789)
esgrfmod2 <- nhlBuild(esgDataRF2[, -1], perc = 1)
esgrfmod3 <- nhlBuild(esgDataRF3[, -1], perc = 1)
esgrfmod4 <- nhlBuild(esgDataRF4[, -1], perc = 1)
esgrfmod5 <- nhlBuild(esgDataRF5[, -1], perc = 1)
esgrfmod6 <- nhlBuild(esgDataRF6[, -1], perc = 1)
esgrfmod7 <- nhlBuild(esgDataRF7[, -1], perc = 1)
esggbmmod1 <- nhlBuild(esgDataGBM1[, -1], type = "gbm", perc = 1)
esggbmmod2 <- nhlBuild(esgDataGBM2[, -1], type = "gbm", perc = 1)
esggbmmod3 <- nhlBuild(esgDataGBM3[, -1], type = "gbm", perc = 1)
esggbmmod4 <- nhlBuild(esgDataGBM4[, -1], type = "gbm", perc = 1)
esggbmmod5 <- nhlBuild(esgDataGBM5[, -1], type = "gbm", perc = 1)
esggbmmod6 <- nhlBuild(esgDataGBM6[, -1], type = "gbm", perc = 1)
esggbmmod7 <- nhlBuild(esgDataGBM7[, -1], type = "gbm", perc = 1)
```

Next we build our meta-data frame from the above predictions.

```{r}
esgrf1 <- predict(esgrfmod1, esgDataRF1)
esgrf2 <- predict(esgrfmod2, esgDataRF2)
esgrf3 <- predict(esgrfmod3, esgDataRF3)
esgrf4 <- predict(esgrfmod4, esgDataRF4)
esgrf5 <- predict(esgrfmod5, esgDataRF5)
esgrf6 <- predict(esgrfmod6, esgDataRF6)
esgrf7 <- predict(esgrfmod7, esgDataRF7)
esgrf <- as.data.frame(cbind(esgDataRF1[, 1], esgrf1, esgrf2, esgrf3, esgrf4,
                             esgrf5, esgrf6, esgrf7))
names(esgrf) <- c("nhl_num", "esgrf1", "esgrf2", "esgrf3", "esgrf4",
                 "esgrf5", "esgrf6", "esgrf7")
esggbm1 <- predict(esggbmmod1, esgDataGBM1)
esggbm2 <- predict(esggbmmod2, esgDataGBM2)
esggbm3 <- predict(esggbmmod3, esgDataGBM3)
esggbm4 <- predict(esggbmmod4, esgDataGBM4)
esggbm5 <- predict(esggbmmod5, esgDataGBM5)
esggbm6 <- predict(esggbmmod6, esgDataGBM6)
esggbm7 <- predict(esggbmmod7, esgDataGBM7)
esggbm <- as.data.frame(cbind(esgDataGBM1[, 1], esggbm1, esggbm2, esggbm3, esggbm4,
                              esggbm5, esggbm6, esggbm7))
names(esggbm) <- c("nhl_num", "esggbm1", "esggbm2", "esggbm3", "esggbm4",
                   "esggbm5", "esggbm6", "esggbm7")
esgData <- merge(esgrf, esggbm, all = TRUE)
esgData <- merge(esgData, esgDataGBM1[, c(1, 26)])
```

Finally, we build our cumulative even strength goal model.

```{r}
esgModel <- nhlBuild(esgData[, -1], type = "gbm", perc = 0.7, seed = 345)
```

We next move on to power play goals.

```{r}
gbmdata <- nhlShape(2012, 2013, outcome = 9)
rfdata <- nhlShape(2013, 2013, outcome = 9)
```

We run our factor analysis function on `pp_goals`.

```{r, cache=TRUE, results='hide'}
ppGoalFactors <- nhlAnalyze(rfdata, gbmdata, seed = 42724)
```

```{r, echo=FALSE}
print(ppGoalFactors)
```

Again, we build data sets.

```{r}
col1 <- c(1:2, 4, 6, 9:10, 15, 24:25, 30, 38:41)
col2 <- c(3, 5, 33:34)
ppgDataRF1 <- nhlShape(2013, 2013, cols = c(col1, col2[1]), outcome = 9, rm.nhlnum = F)
ppgDataRF2 <- nhlShape(2013, 2013, cols = c(col1, col2[2]), outcome = 9, rm.nhlnum = F)
ppgDataRF3 <- nhlShape(2013, 2013, cols = c(col1, col2[3]), outcome = 9, rm.nhlnum = F)
ppgDataRF4 <- nhlShape(2013, 2013, cols = c(col1, col2[4]), outcome = 9, rm.nhlnum = F)
ppgDataRF5 <- nhlShape(2013, 2013, cols = c(col1, col2), outcome = 9, rm.nhlnum = F)
ppgDataGBM1 <- nhlShape(2012, 2013, cols = c(col1, col2[1]), outcome = 9,
                       rm.nhlnum = F, rm.NA = FALSE)
ppgDataGBM1 <- subset(ppgDataGBM1, !is.na(goals.1))
ppgDataGBM2 <- nhlShape(2012, 2013, cols = c(col1, col2[2]), outcome = 9,
                       rm.nhlnum = F, rm.NA = FALSE)
ppgDataGBM2 <- subset(ppgDataGBM2, !is.na(goals.1))
ppgDataGBM3 <- nhlShape(2012, 2013, cols = c(col1, col2[3]), outcome = 9,
                       rm.nhlnum = F, rm.NA = FALSE)
ppgDataGBM3 <- subset(ppgDataGBM3, !is.na(goals.1))
ppgDataGBM4 <- nhlShape(2012, 2013, cols = c(col1, col2[4]), outcome = 9,
                       rm.nhlnum = F, rm.NA = FALSE)
ppgDataGBM4 <- subset(ppgDataGBM4, !is.na(goals.1))
ppgDataGBM5 <- nhlShape(2012, 2013, cols = c(col1, col2), outcome = 9,
                       rm.nhlnum = F, rm.NA = FALSE)
ppgDataGBM5 <- subset(ppgDataGBM5, !is.na(goals.1))
```

We build our pre-models from them.

```{r, cache=TRUE, results='hide'}
ppgrfmod1 <- nhlBuild(ppgDataRF1[, -1], perc = 1, seed = 15793)
ppgrfmod2 <- nhlBuild(ppgDataRF2[, -1], perc = 1)
ppgrfmod3 <- nhlBuild(ppgDataRF3[, -1], perc = 1)
ppgrfmod4 <- nhlBuild(ppgDataRF4[, -1], perc = 1)
ppgrfmod5 <- nhlBuild(ppgDataRF5[, -1], perc = 1)
ppggbmmod1 <- nhlBuild(ppgDataGBM1[, -1], type = "gbm", perc = 1)
ppggbmmod2 <- nhlBuild(ppgDataGBM2[, -1], type = "gbm", perc = 1)
ppggbmmod3 <- nhlBuild(ppgDataGBM3[, -1], type = "gbm", perc = 1)
ppggbmmod4 <- nhlBuild(ppgDataGBM4[, -1], type = "gbm", perc = 1)
ppggbmmod5 <- nhlBuild(ppgDataGBM5[, -1], type = "gbm", perc = 1)
```

Next we build our meta-data frame from the above predictions.

```{r}
ppgrf1 <- predict(ppgrfmod1, ppgDataRF1)
ppgrf2 <- predict(ppgrfmod2, ppgDataRF2)
ppgrf3 <- predict(ppgrfmod3, ppgDataRF3)
ppgrf4 <- predict(ppgrfmod4, ppgDataRF4)
ppgrf5 <- predict(ppgrfmod5, ppgDataRF5)
ppgrf <- as.data.frame(cbind(ppgDataRF1[, 1], ppgrf1, ppgrf2, ppgrf3, ppgrf4, ppgrf5))
names(ppgrf) <- c("nhl_num", "ppgrf1", "ppgrf2", "ppgrf3", "ppgrf4", "ppgrf5")
ppggbm1 <- predict(ppggbmmod1, ppgDataGBM1)
ppggbm2 <- predict(ppggbmmod2, ppgDataGBM2)
ppggbm3 <- predict(ppggbmmod3, ppgDataGBM3)
ppggbm4 <- predict(ppggbmmod4, ppgDataGBM4)
ppggbm5 <- predict(ppggbmmod5, ppgDataGBM5)
ppggbm <- as.data.frame(cbind(ppgDataGBM1[, 1], ppggbm1, ppggbm2, ppggbm3, ppggbm4, ppggbm5))
names(ppggbm) <- c("nhl_num", "ppggbm1", "ppggbm2", "ppggbm3", "ppggbm4", "ppggbm5")
ppgData <- merge(ppgrf, ppggbm, all = TRUE)
ppgData <- merge(ppgData, ppgDataGBM1[, c(1, 28)])
```

Finally, we build our power play goal model.

```{r}
ppgModel <- nhlBuild(ppgData[, -1], type = "gbm", perc = 0.7, seed = 7829)
```

Lastly we model short-handed goals.

```{r}
gbmdata <- nhlShape(2012, 2013, outcome = 11)
rfdata <- nhlShape(2013, 2013, outcome = 11)
```

We run our factor analysis function on `sh_goals`.

```{r, cache=TRUE, results='hide'}
shGoalFactors <- nhlAnalyze(rfdata, gbmdata, seed = 52825)
```

```{r, echo=FALSE}
print(shGoalFactors)
```

Again, we build data sets.

```{r}
col1 <- c(1:2, 4, 12, 15:16, 32:34, 39, 42)
col2 <- c(11, 24, 29, 41)
shgDataRF1 <- nhlShape(2013, 2013, cols = c(col1, col2[1]), outcome = 11, rm.nhlnum = F)
shgDataRF2 <- nhlShape(2013, 2013, cols = c(col1, col2[2]), outcome = 11, rm.nhlnum = F)
shgDataRF3 <- nhlShape(2013, 2013, cols = c(col1, col2[3]), outcome = 11, rm.nhlnum = F)
shgDataRF4 <- nhlShape(2013, 2013, cols = c(col1, col2[4]), outcome = 11, rm.nhlnum = F)
shgDataRF5 <- nhlShape(2013, 2013, cols = c(col1, col2), outcome = 11, rm.nhlnum = F)
shgDataGBM1 <- nhlShape(2012, 2013, cols = c(col1, col2[1]), outcome = 11,
                       rm.nhlnum = F, rm.NA = FALSE)
shgDataGBM1 <- subset(shgDataGBM1, !is.na(goals.1))
shgDataGBM2 <- nhlShape(2012, 2013, cols = c(col1, col2[2]), outcome = 11,
                       rm.nhlnum = F, rm.NA = FALSE)
shgDataGBM2 <- subset(shgDataGBM2, !is.na(goals.1))
shgDataGBM3 <- nhlShape(2012, 2013, cols = c(col1, col2[3]), outcome = 11,
                       rm.nhlnum = F, rm.NA = FALSE)
shgDataGBM3 <- subset(shgDataGBM3, !is.na(goals.1))
shgDataGBM4 <- nhlShape(2012, 2013, cols = c(col1, col2[4]), outcome = 11,
                       rm.nhlnum = F, rm.NA = FALSE)
shgDataGBM4 <- subset(shgDataGBM4, !is.na(goals.1))
shgDataGBM5 <- nhlShape(2012, 2013, cols = c(col1, col2), outcome = 11,
                       rm.nhlnum = F, rm.NA = FALSE)
shgDataGBM5 <- subset(shgDataGBM5, !is.na(goals.1))
```

We build our pre-models from them.

```{r, cache=TRUE, results='hide'}
shgrfmod1 <- nhlBuild(shgDataRF1[, -1], perc = 1, seed = 2742, distribution = "poisson")
shgrfmod2 <- nhlBuild(shgDataRF2[, -1], perc = 1, distribution = "poisson")
shgrfmod3 <- nhlBuild(shgDataRF3[, -1], perc = 1, distribution = "poisson")
shgrfmod4 <- nhlBuild(shgDataRF4[, -1], perc = 1, distribution = "poisson")
shgrfmod5 <- nhlBuild(shgDataRF5[, -1], perc = 1, distribution = "poisson")
shggbmmod1 <- nhlBuild(shgDataGBM1[, -1], type = "gbm", perc = 1, distribution = "poisson")
shggbmmod2 <- nhlBuild(shgDataGBM2[, -1], type = "gbm", perc = 1, distribution = "poisson")
shggbmmod3 <- nhlBuild(shgDataGBM3[, -1], type = "gbm", perc = 1, distribution = "poisson")
shggbmmod4 <- nhlBuild(shgDataGBM4[, -1], type = "gbm", perc = 1, distribution = "poisson")
shggbmmod5 <- nhlBuild(shgDataGBM5[, -1], type = "gbm", perc = 1, distribution = "poisson")
```

Next we build our meta-data frame from the above predictions.

```{r}
shgrf1 <- predict(shgrfmod1, shgDataRF1, type = "response")
shgrf2 <- predict(shgrfmod2, shgDataRF2, type = "response")
shgrf3 <- predict(shgrfmod3, shgDataRF3, type = "response")
shgrf4 <- predict(shgrfmod4, shgDataRF4, type = "response")
shgrf5 <- predict(shgrfmod5, shgDataRF5, type = "response")
shgrf <- as.data.frame(cbind(shgDataRF1[, 1], shgrf1, shgrf2, shgrf3, shgrf4, shgrf5))
names(shgrf) <- c("nhl_num", "shgrf1", "shgrf2", "shgrf3", "shgrf4", "shgrf5")
shggbm1 <- predict(shggbmmod1, shgDataGBM1, type = "response")
shggbm2 <- predict(shggbmmod2, shgDataGBM2, type = "response")
shggbm3 <- predict(shggbmmod3, shgDataGBM3, type = "response")
shggbm4 <- predict(shggbmmod4, shgDataGBM4, type = "response")
shggbm5 <- predict(shggbmmod5, shgDataGBM5, type = "response")
shggbm <- as.data.frame(cbind(shgDataGBM1[, 1], shggbm1, shggbm2, shggbm3, shggbm4, shggbm5))
names(shggbm) <- c("nhl_num", "shggbm1", "shggbm2", "shggbm3", "shggbm4", "shggbm5")
shgData <- merge(shgrf, shggbm, all = TRUE)
shgData <- merge(shgData, shgDataGBM1[, c(1, 22)])
```

Finally, we build our power play goal model.

```{r}
shgModel <- nhlBuild(shgData[, -1], type = "gbm", perc = 0.7, seed = 7829, distribution = "poisson")
```
